---
title: "Random_search"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Random_search}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(calibrater)
```

This code was created by the DARTH workgroup (www.darthworkgroup.com). When using or modifying this code, please do so with attribution and cite our publications:

Alarid-Escudero F, Maclehose RF, Peralta Y, Kuntz KM, Enns EA. Non-identifiability in model calibration and implications for medical decision making. Med Decis Making. 2018; 38(7):810-821.

Jalal H, Pechlivanoglou P, Krijkamp E, Alarid-Escudero F, Enns E, Hunink MG. An Overview of R in Health Decision Sciences. Med Decis Making. 2017; 37(3): 735-746.

A walkthrough of the code could be found in the follwing link:
- https://darth-git.github.io/calibSMDM2018-materials/

# Calibration Specifications  

Model: 3-State Cancer Relative Survival (CRS) Markov Model
Inputs to be calibrated: `p_Mets, p_DieMets`
Targets: `Surv`

# Search method: 

Random search using:
- Full factorial grid
- Random grid
- Latin-Hypercube Sampling

# Goodness-of-fit measure: 

- Sum of log-likelihoods
- Sum of squared errors

# Load packages and function files:

```{r, echo=FALSE}
# General purposes:
pacman::p_load(devtools, testthat, usethis, tidyverse)
devtools::load_all()
# Sampling data:
pacman::p_load(lhs)
# Visualisation:
pacman::p_load(plotrix, psych)
```

# Load target data:

```{r, echo=FALSE}
load(file.path(here::here(), "data", "CRS_targets.rda"))
lst_targets <- CRS_targets
```

# Visualise target data:

```{r Visualise the target}
# Plotting target data - survival ("Surv"):
targets_pt = ggplot(data = lst_targets$Surv,
                    aes(x = time,
                        y = value)) +
  geom_errorbar(aes(ymin = lb, ymax = ub)) +
  geom_point() +
  theme(
    panel.border = element_rect(fill = NA, color = 'black')
  ) + 
  labs(title = "Calibration target",
       x = "Time",
       y = "Proportion survived")
targets_pt
targets_pt2 = ggplot(data = lst_targets$Surv,
                     aes(x = time,
                         y = value)) +
  geom_line() +
  geom_line(aes(x = time, y = lb), linetype = 'dashed', color = 'red',
            show.legend = TRUE) +
  geom_line(aes(x = time, y = ub), linetype = 'dashed', color = 'red',
            show.legend = TRUE) +
  scale_color_manual(values = c('black', 'red', 'red'),
                     breaks = c('value', 'lb', 'ub'),
                     labels = c('Survival', '95% CI', '95% CI')) +
  theme(
    panel.border = element_rect(fill = NA, color = 'black')
  ) + 
  labs(title = "Calibration target",
       x = "Time",
       y = "Proportion survived")
targets_pt2
```

# The model is defined as a function, testing that it works:

- inputs are proposed parameters to be estimated through calibration
- outputs correspond to the target data

```{r Test the model:}
# Check that the model works:
v_params_test <- c(p_Mets = 0.10, p_DieMets = 0.05) # true values
# Check that inputs are handled correctly, by using true values:
compare(CRS_markov(v_params = v_params_test), CRS_markov())

# Compare outputs of default values to the targets:
targets_pt +
  geom_line(data = as_tibble(CRS_markov()) %>%
              mutate(time = cbind(lst_targets$Surv$time)), 
            aes(x = time, y = Surv),
            color = 'red') +
  scale_color_manual(values = c('Surv' = "red"))
```

# Specify calibration parameters:

```{r Specify parameters:}
# Specify seed (for reproducible sequence of random numbers)
set.seed(1)

# Number of random samples
n_samples <- 1000

# Names and number of input parameters to be calibrated
v_params_names <- c("p_Mets", "p_DieMets")
n_params <- length(v_params_names)

# Range on input search space
lb <- c(p_Mets = 0.04, p_DieMets = 0.04) # lower bound
ub <- c(p_Mets = 0.16, p_DieMets = 0.16) # upper bound

# Number of calibration targets
v_target_names <- c("Surv")
n_target <- length(v_target_names)
```

# Calibrate:

## Calibration settings and sample propose values:

```{r Set calibration and sample proposed values:}
## Generate a random sample of input values:
### Full factorial grid search:
grid_points <- pmap_dfc(.l = list(v_params_names, lb, ub), 
                        .f = function(.x, .y, .z) {
                          assign(.x, seq(from = .y, to = .z, 
                                         length.out = n_samples))
                        })
m_param_samp_fgs <- do.call(expand.grid, grid_points)

# ggplot(m_param_samp_fgs) +
#   geom_point(aes(x = p_Mets, y = p_DieMets), shape = 21, size = 1) +
#   theme(
#     panel.border = element_rect(fill = NA, color = 'black')
#   )

### Random grid search:
params_args <- tibble(vars = v_params_names,
                      fs = c("runif", "runif"),
                      args = pmap(.l = list(n_samples, lb, ub), 
                                  .f = function(.x, .y, .z) {
                                    list(n = .x, min = .y, max = .z)
                                  }))

m_param_samp_rgs <- pmap_dfc(.l = list(params_args$vars,
                                       params_args$fs, 
                                       params_args$args),
                         .f = function(name, fn, arg) {
                           assign(name,
                                  exec(.fn = fn, !!!arg))
                         })

# ggplot(m_param_samp_rgs) +
#   geom_point(aes(x = p_Mets, y = p_DieMets), shape = 21, size = 1) +
#   theme(
#     panel.border = element_rect(fill = NA, color = 'black')
#   )

### Latin Hypercube Sampling (LHS) grid search:
#### Sample unit Latin Hypercube:
m_lhs_unit <- lhs::randomLHS(n_samples, n_params)

#### Rescale to min/max of each parameter:
m_param_samp_lhs <- matrix(nrow = n_samples, ncol = n_params)
for (i in 1:n_params) {
  m_param_samp_lhs[,i] <- qunif(m_lhs_unit[,i],
                                min = lb[i],
                                max = ub[i])
}
colnames(m_param_samp_lhs) <- v_params_names

#### Choose the search strategy:
m_param_samp <- m_param_samp_lhs

### Visualise sampled parameter sets:
pairs.panels(m_param_samp)
```

## Run the model using all proposed parameter sets and record predicted values:

```{r Run model and record predicted values}
## Record start time of calibration:
t_init <- Sys.time()

## Initialize goodness-of-fit vector
m_GOF_llk <- m_GOF_sse <- matrix(nrow = n_samples, ncol = n_target)
colnames(m_GOF_llk) <- colnames(m_GOF_sse) <- paste0(v_target_names, "_fit")

## Loop through sampled sets of input values
for (j in 1:n_samples) {
  
  ### Run model for a given parameter set:
  model_res <- CRS_markov(v_params = m_param_samp[j, ])
  
  ### Calculate goodness-of-fit of model outputs to targets:
  
  ### TARGET 1: Survival ("Surv")
  ### Log likelihood:
  m_GOF_llk[j, 1] <- sum(dnorm(x = lst_targets$Surv$value,
                               mean = model_res$Surv,
                               sd = lst_targets$Surv$se,
                               log = TRUE))
  
  ### Weighted sum of squared errors:
  w <- 1/(lst_targets$Surv$se^2)
  m_GOF_sse[j, 1] <- -sum(w * (lst_targets$Surv$value - model_res$Surv)^2)
  
} # End loop over sampled parameter sets

```

## Combine fits to the different targets into single GOF:

```{r Combine fits to different targets to get a single GOF}
## Different targets can have different weights: here all have same weight
v_weights <- matrix(1, nrow = n_target, ncol = 1)

## Calculate weighted sum of each GOF row by matrix multiplication:
v_GOF_overall_llk <- m_GOF_llk %*% v_weights
v_GOF_overall_sse <- m_GOF_sse %*% v_weights

## Store in GOF matrix with column name "Overall"
m_GOF_llk <- m_GOF_llk %>% 
  as_tibble() %>% 
  mutate('Overall_fit' = v_GOF_overall_llk)
m_GOF_sse <- m_GOF_sse %>% 
  as_tibble() %>% 
  mutate('Overall_fit' = v_GOF_overall_sse)

## Calculate computation time
comp_time <- Sys.time() - t_init
comp_time
```

## Exploring best-fitting input sets:

```{r Find best-fitting input sets}
## Arrange parameter sets in order of fit:
m_calib_res_llk <- cbind(m_param_samp, m_GOF_llk)
m_calib_res_sse <- cbind(m_param_samp, m_GOF_sse)

## Sort in descending order for LLK and ascending for SSE:   
m_calib_res_llk <- m_calib_res_llk %>% 
  arrange(desc(Overall_fit))
m_calib_res_sse <- m_calib_res_sse %>% 
  arrange(desc(Overall_fit))

## Examine the top 10 best-fitting sets:
m_calib_res_llk[1:10,]
m_calib_res_sse[1:10,]

# Plot the top 100 (top 10%):
ggplot() +
  geom_point(data = m_calib_res_sse[1:100,],
             aes(x = p_Mets,
                 y = p_DieMets)) +
  theme(
    panel.border = element_rect(fill = NA, colour = 'black')
  ) +
  labs(title = "SSE parameters")

ggplot() +
  geom_point(data = m_calib_res_llk[1:100,],
             aes(x = p_Mets,
                 y = p_DieMets)) +
  theme(
    panel.border = element_rect(fill = NA, colour = 'black')
  ) +
  labs(title = "Likelihood parameters")

# Pairwise comparison of top 100 sets:
pairs.panels(m_calib_res_llk[1:100, v_params_names])
pairs.panels(m_calib_res_sse[1:100, v_params_names])

# Plot model-predicted output at best set vs targets:
v_out_best_llk <- CRS_markov(m_calib_res_llk[1,])
v_out_best_sse <- CRS_markov(m_calib_res_sse[1,])

targets_pt +
  geom_point(data = tibble('Likelihood' = v_out_best_llk$Surv) %>%
               mutate('SSE' = v_out_best_sse$Surv,
                      'time' = cbind(lst_targets$Surv$time)) %>% 
               pivot_longer(cols = -time, names_to = 'GOF', 
                            values_to = 'Survival'),
             aes(x = time, y = Survival, color = GOF, shape = GOF), 
             alpha = 0.5)
```
